Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-07-28 paper/aap-pediatrics-cover.tex
Typo
Duplicative work

I am pleased to submit an original research article titled \textit{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013} by Ben Artin, Virginia E. Pitzer, an Daniel M. Weinberger for consideration for publication in \textit{Pediatrics}. The American Academyc of Pediatrics makes recommendations about when to start prophylaxis against RSV. Aside from Florida, the recommended start date is the same for the entire US. Using county-level data from Connecticut, we considered whether a recommended start date that varies by state or county would provide any benefit compared with the national recommendation. We find that a state-specific prophylaxis regimen would confer a modest improvement over the current AAP-recommended regimen. This general approach could be used to evaluate the timing of prophylaxis in other states as well.

@@

>>>>

I am pleased to submit an original research article titled \textit{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013} by Ben Artin, Virginia E. Pitzer, an Daniel M. Weinberger for consideration for publication in \textit{Pediatrics}. The American Academy of Pediatrics makes recommendations about when to start prophylaxis against RSV. Aside from Florida, the recommended start date is the same for the entire US. Using county-level data from Connecticut, we considered whether a recommended start date that varies by state or county would provide any benefit compared with the national recommendation. We find that a state-specific prophylaxis regimen would confer a modest improvement over the current AAP-recommended regimen. This general approach could be used to evaluate the timing of prophylaxis in other states as well.

@@

The same data was used in: Noveroske Douglas Brian. Respiratory syncytial virus in Connecticut: Predictors of seasonal epidemic timing \textit{Public Health Theses}. 2016.
